#Calling libraries
```{r}
library(tidyverse)
library(ggplot2)
```

# Problem 1
```{r}
#install.packages("palmerpenguins")

data("penguins", package = "palmerpenguins")

first_scatterplot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
first_scatterplot

ggsave("first_scatterplot.pdf")
```
- This dataset is about penguins and has the following variables: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year.
- This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns
- The mean flipper length is `r mean(penguins$flipper_length_mm,na.rm=TRUE)` mm. 

# Problem 2
```{r}
set.seed(1289)

new_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("first", "second", "third", "third", "second", "first", "first", "second", "third", "second"))
)
new_df

mean(new_df$vec_numeric)
mean(new_df$vec_logical)
mean(new_df$vec_char) 
mean(new_df$vec_factor)

```

We are able to take the mean of the numeric and logical variables but not of the character and factor variables.

```{r, results = FALSE}
logical_new_col <- as.numeric(new_df$vec_logical)

char_new_col <- as.numeric(new_df$vec_char)

factor_new_col <- as.numeric(new_df$vec_factor)

mean(char_new_col)
mean(factor_new_col)
```
After converting the character and factor variables to numeric type, we are able to take their mean. The mean for the new character variable is `r mean(char_new_col)` and the mean for the new factor variable is `r mean(factor_new_col)`.
